\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-02-19 doc/publications/plos16/plos16.tex
small change cption in paper

\begin{figure}[tbhp]
  \begin{adjustwidth}{-1.00in}{0in}
    \caption{\textbf{Runtime comparison on the 1000 genomes project}}
    \label{figure:1000genomes}
    \includegraphics[totalheight=8cm]{./figs/1000genomesRuntime.pdf}
    \begin{flushleft}
      The figure shows the runtime for the 5 subsets of the 1000 genomes project and the different methods investigated.
      $\bigotimes$ marks the last dataset the different method completed before running out of memory or running more than
      24 hours. The dashed lines mark the trajectory for how ranger and Spark ML had performed given larger memory machines.
    \end{flushleft}
  \end{adjustwidth}
\end{figure}

>>>>

\begin{figure}[tbhp]
  \begin{adjustwidth}{-1.00in}{0in}
    \caption{\textbf{Runtime comparison on the 1000 genomes project}}
    \label{figure:1000genomes}
    \includegraphics[totalheight=8cm]{./figs/1000genomesRuntime.pdf}
    \begin{flushleft}
      The figure shows the runtime for the 5 subsets of the 1000 genomes project and the different methods investigated.
      $\bigotimes$ marks the last dataset the different method completed before running out of memory or running more than
      20 hours. The dashed lines mark the trajectory for how \ranger and Spark ML had performed given larger memory machines.
    \end{flushleft}
  \end{adjustwidth}
\end{figure}
